---
title: "Iteration and Listcols"
author: "Talea Cornelius"
date: "11/6/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)

set.seed(1)
```


In R, vectors are limited to a single data class – all elements are characters, or all numeric, or all logical. Trying to join the following vectors will result in coersion, as would creating vectors of mixed types.

```{r}
vec_numeric = 5:8
vec_char = c("My", "name", "is", "Jeff")
vec_logical = c(TRUE, TRUE, TRUE, FALSE)
```

Lists provide a way to store anything you want. This flexibility is great, but is offset by a certain … clunkiness. Lists contain indexed elements, and the indexed elements themselves be scalars, vectors, or other things entirely.

```{r}
l = list(
  vec_numeric = 5:8,
  mat         = matrix(1:8, 2, 4),
  vec_logical = c(TRUE, FALSE),
  summary     = summary(rnorm(1000)))
l
```

```{r}
l$vec_numeric
l[[1]]
l[[1]][1:3]
```

```{r}
list_norms = 
  list(
    a = rnorm(20, 3, 1),
    b = rnorm(20, 0, 5),
    c = rnorm(20, 10, .2),
    d = rnorm(20, -3, 1)
  )

is.list(list_norms)
```
```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Cannot be computed for length 1 vectors")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)

  tibble(
    mean = mean_x, 
    sd = sd_x
  )
}
```

```{r}
mean_and_sd(list_norms[[1]])
mean_and_sd(list_norms[[2]])
mean_and_sd(list_norms[[3]])
mean_and_sd(list_norms[[4]])
```

```{r}
output = vector("list", length = 4)

for (i in 1:4) {
  output[[i]] = mean_and_sd(list_norms[[i]])
}
```

```{r}
output = map(list_norms, mean_and_sd)
```

The first argument to map is the list (or vector, or data frame) we want to iterate over, and the second argument is the function we want to apply to each element. The line above will produce the same output as the previous loop, but is clearer and easier to understand (once you’re used to map …).

It’s sometimes necessary to be more specific in giving arguments to map. In particular, using .x = list_norms for the input list and ~ mean_and_sd(.x) to specify the function applied to the input list (using .x as a placeholder) will produce the same result.

```{r}
output = map(.x = list_norms, ~ mean_and_sd(.x))
output
```

This code (using map) is why we pointed out in writing functions that functions can be passed as arguments to other functions. The second argument in map(list_norms, mean_and_sd) is a function we just wrote. To see how powerful this can be, suppose we wanted to apply a different function, say median, to each column of list_norms. The chunk below includes both the loop and the map approach.

```{r}
output = vector("list", length = 4)

for (i in 1:4) {
  output[[i]] = median(list_norms[[i]])
}

output = map(list_norms, median)
output
# output = map(.x = list_norms, ~ median(.x))
```

Again, both options produce the same output, but the map places the focus squarely on the function you want to apply by removing much of the bookkeeping.

map variants

There are some useful variants to the basic map function if you know what kind of output you’re going to produce. Below we use map_dbl because median outputs a single numeric value each time; the result is a vector instead of a list. Using the .id argument keeps the names of the elements in the input list.

```{r}
output = map_dbl(list_norms, median, .id = "input")
```

If we tried to use map_int or map_lgl, we’d get an error because the output of median isn’t a integer or a logical. This is a good way to help catch mistakes when they arise.

Similarly, since we know mean_and_sd produces a data frame, we can use the output-specific map_dfr; this will produce a single data frame.

```{r}
output = map_dfr(list_norms, mean_and_sd, .id = "input")
```

The map_df variants can be helpful when your map statement is part of a longer chain of piped commands.

Lastly, the variant map2 (and map2_dbl, etc) is helpful when your function has two arguments. In these cases, I find it best to be specific about arguments using something like the following:

```{r}
output = map2(.x = input_1, .y = input_2, ~func(arg_1 = .x, arg_2 = .y))
```


```{r}
listcol_df = 
  tibble(
    name = c("a", "b", "c", "d"),
    samp = list_norms
  )
```


```{r}
listcol_df %>% pull(samp)

listcol_df$samp[[1]]
```

You will need to be able to manipulate list columns, but usual operations for columns that might appear in mutate (like mean or recode) often don’t apply to the entries in a list column. Instead, recognizing list columns as list columns motivates an approach for working with them.

Let’s apply mean_and_sd to the first element of our list column.

```{r}
mean_and_sd(listcol_df$samp[[1]])
map(listcol_df$samp, mean_and_sd)
```
The map function returns a list; we could store the results as a new list column … !!!

We’ve been using mutate to define a new variable in a data frame, especially one that is a function of an existing variable. That’s exactly what we will keep doing.

```{r}
listcol_df = 
  listcol_df %>% 
  mutate(summary = map(samp, mean_and_sd))

listcol_df
```


Shifting gears a bit, let’s revisit the weather data from visualization and elsewhere; these data consist of one year of observations from three monitoring stations. The code below pulls these data into R (using the rnoaa package, which interacts with the NOAA API).


```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

The station name and id are constant across the year’s temperature and precipitation data. For that reason, we can reorganize these data into a new data frame with a single row for each station. Weather data will be separated into three station-specific data frames, each of which is the data “observation” for the respective station.

```{r}
weather_nest = 
  nest(weather_df, data = date:tmin)

weather_nest
weather_nest %>% pull(name)
weather_nest %>% pull(data)
```

```{r}
unnest(weather_nest, cols = data)
```


```{r}
weather_lm = function(df) {
  lm(tmax ~ tmin, data = df)
}
```

```{r}
weather_lm(weather_nest$data[[1]])
```

```{r}
map(weather_nest$data, weather_lm)
```

As an aside, you can avoid the creation of a dedicated function using map’s syntax for “anonymous” (i.e. not named and saved) functions. This is fine for really short operations, but I typically write a dedicated function instead of using this option.

```{r}
map(weather_nest$data, ~lm(tmax ~ tmin, data = .x))
```


```{r}
weather_nest = 
  weather_nest %>% 
  mutate(models = map(data, weather_lm))

weather_nest
```

This is great! We now have a data frame that has rows for each station; columns contain weather datasets and fitted models. This makes it very easy to keep track of models across stations, and to perform additional analyses.

This is, for sure, a fairly complex bit of code, but in just a few lines we’re able to fit separate linear models to each of our stations. And, once you get used to list columns, map, and the rest of it, these lines of code are pretty clear and can be extended to larger datasets with more complex structures.

Revisiting Napoleon

In reading data from the web and elsewhere, we wrote code that allowed us to scrape information in Amazon reviews; in writing functions we wrapped that code into a function called read_page_reviews which, for a given url, produces a data frame containing review titles, star ratings, and text.

```{r}
library(rvest)
```

```{r}
read_page_reviews = function(url) {
  
  html = read_html(url)
  
  title = 
    html %>%
    html_nodes("#cm_cr-review_list .review-title") %>%
    html_text()
  
  stars = 
    html %>%
    html_nodes("#cm_cr-review_list .review-rating") %>%
    html_text() %>%
    str_extract("\\d") %>%
    as.numeric()
  
  text = 
    html %>%
    html_nodes(".review-data:nth-child(5)") %>%
    html_text()
  
  tibble(title, stars, text)
}
```

```{r}
url_base = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="
vec_urls = str_c(url_base, 1:5)
```

```{r}
output = vector("list", 5)

for (i in 1:5) {
  output[[i]] = read_page_reviews(vec_urls[[i]])
}

dynamite_reviews = bind_rows(output)

dynamite_reviews = map_df(vec_urls, read_page_reviews)
```

```{r}
dynamite_reviews = 
  tibble(
    page = 1:5,
    urls = str_c(url_base, page)) %>% 
  mutate(reviews = map(urls, read_page_reviews)) %>% 
  unnest()
```














