---
title: "Writing Functions"
author: "Talea Cornelius"
date: "11/6/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rvest)
```

```{r}
set.seed(1)
```


```{r}
x_vec = rnorm(25, mean = 5, sd = 3)

(x_vec - mean(x_vec)) / sd(x_vec)
```
```{r}
z_scores = function(x) {
  
  z = (x - mean(x)) / sd(x)
  z
  
}

z_scores(x_vec)
```

To avoid behavior you don’t want (i.e. to “fail noisily and as soon as possible”) we’ll add some checks on the argument values using conditional statements.

```{r}
z_scores = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Z scores cannot be computed for length 1 vectors")
  }
  
  z = mean(x) / sd(x)
  
  z
}
```

```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Cannot be computed for length 1 vectors")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)

  list(mean = mean_x, 
       sd = sd_x)
}
```

```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Cannot be computed for length 1 vectors")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)

  tibble(
    mean = mean_x, 
    sd = sd_x
  )
}
```


I’d like to have a function that takes a given sample size along with a true mean and standard deviation, simulates data from a normal distribution, and returns the estimated mean and standard deviation. I’ll start from the code below.

```{r}
sim_data = tibble(
  x = rnorm(30, mean = 2, sd = 3)
)

sim_data %>% 
  summarize(
    mu_hat = mean(x),
    sigma_hat = sd(x)
  )
```

```{r}
sim_mean_sd = function(n, mu = 2, sigma = 3) {
  
  sim_data = tibble(
    x = rnorm(n, mean = mu, sd = sigma),
  )
  
  sim_data %>% 
    summarize(
      mu_hat = mean(x),
      sigma_hat = sd(x)
    )
}
```

```{r}
sim_mean_sd(3,2,3)
sim_mean_sd(30,2,3)
sim_mean_sd(300,2,3)
sim_mean_sd(3000,2,3)
```

In reading data from the web, we wrote code that allowed us to scrape information in Amazon reviews. That code is below.

```{r}
url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"

dynamite_html = read_html(url)

review_titles = 
  dynamite_html %>%
  html_nodes(".a-text-bold span") %>%
  html_text()

review_stars = 
  dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-rating") %>%
  html_text() %>%
  str_extract("^\\d") %>%
  as.numeric()

review_text = 
  dynamite_html %>%
  html_nodes(".review-text-content span") %>%
  html_text() %>% 
  str_replace_all("\n", "") %>% 
  str_trim()

reviews = tibble(
  title = review_titles,
  stars = review_stars,
  text = review_text
)
```

Let’s write a quick function to scrape review information for any URL to an Amazon review page.

```{r}
read_page_reviews <- function(url) {
  
  html = read_html(url)
  
  review_titles = 
    html %>%
    html_nodes(".a-text-bold span") %>%
    html_text()
  
  review_stars = 
    html %>%
    html_nodes("#cm_cr-review_list .review-rating") %>%
    html_text() %>%
    str_extract("^\\d") %>%
    as.numeric()
  
  review_text = 
    html %>%
    html_nodes(".review-text-content span") %>%
    html_text() %>% 
    str_replace_all("\n", "") %>% 
    str_trim()
  
  tibble(
    title = review_titles,
    stars = review_stars,
    text = review_text
  )
}
```

Next we’ll use this to read in reviews from a few pages and combine the results.

```{r}
url_base = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="
vec_urls = str_c(url_base, 1:5)

dynamite_reviews = bind_rows(
  read_page_reviews(vec_urls[1]),
  read_page_reviews(vec_urls[2]),
  read_page_reviews(vec_urls[3]),
  read_page_reviews(vec_urls[4]),
  read_page_reviews(vec_urls[5])
)

dynamite_reviews
```

In tidy data, we broke the “only copy code twice” rule when we used the code below to process the LoTR words data:

```{r}
fellowship_ring = readxl::read_excel("./data/LotR_Words.xlsx", range = "B3:D6") %>%
  mutate(movie = "fellowship_ring")

two_towers = readxl::read_excel("./data/LotR_Words.xlsx", range = "F3:H6") %>%
  mutate(movie = "two_towers")

return_king = readxl::read_excel("./data/LotR_Words.xlsx", range = "J3:L6") %>%
  mutate(movie = "return_king")

lotr_tidy = bind_rows(fellowship_ring, two_towers, return_king) %>%
  janitor::clean_names() %>%
  gather(key = sex, value = words, female:male) %>%
  mutate(race = str_to_lower(race)) %>% 
  select(movie, everything()) 
```

```{r}
lotr_load_and_tidy = function(path, range, movie_name) {
  
  df = readxl::read_excel(path, range = range) %>%
    janitor::clean_names() %>%
    gather(key = sex, value = words, female:male) %>%
    mutate(race = str_to_lower(race),
           movie = movie_name)
  
  df
  
}

lotr_tidy = 
  bind_rows(
    lotr_load_and_tidy("./data/LotR_Words.xlsx", "B3:D6", "fellowship_ring"),
    lotr_load_and_tidy("./data/LotR_Words.xlsx", "F3:H6", "two_towers"),
    lotr_load_and_tidy("./data/LotR_Words.xlsx", "J3:L6", "return_king")) %>%
  select(movie, everything()) 
```

```{r}
x_vec = rnorm(25, 0, 1)

my_summary = function(x, summ_func) {
  summ_func(x)
}

my_summary(x_vec, sd)
```


```{r}
my_summary(x_vec, IQR)
my_summary(x_vec, var)
```

```{r}
f = function(x) {
  z = x + y
  z
}

x = 1
y = 2

f(x = y)
```














